Morphological Operations Applied to Crack Detection in Digital Art Restoration

### 2014-03-24 LaTeX Paper/paper.tex
Fine tuning...

\section{Morphological Operations}\label{morphological operations}
Following optional edge detection is crack detection, the focus of this paper. However, in order to understand this stage, it is first necessary to describe the basic principles of mathematical morphology. Typically, morphology is used in processing binary (black and white) images, although there are also variations used for greyscale images. This paper will examine both variations. Morphological functions take two inputs. The first input is the image to be processed. In binary morphology, the input image is divided into foreground (typically white) and background (typically black) regions. In greyscale morphology, the image is treated as a three-dimensional surface, where higher areas are brighter (white) and lower areas are darker (black). The second input is a structuring element, a (typically small, in comparison to the image) set of coordinate points. An example of a 3x3 square structuring element with the origin located at the center in comparison to both a 30x20 binary image and an 11x32 greyscale image is presented in Figure~\ref{structuring element figure}. The structuring element is then used to modify the input image. The image that results from the morphological operation is determined by the shape, size, and point of origin of the structuring element~\cite{MorphologyWikiAnonymous, MorphologyBook:2000, MorphologyPaper:1987, MorphologyWiki}. Subsections~\ref{erosion}, \ref{dilation}, \ref{opening}, and \ref{closing} explain the fundamental operations of mathematical morphology.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 6.5in 0 0},clip]{structuring_element}
\caption{Structuring Elements: Top: Structuring Element. Bottom Left: Structuring Element in Comparison to Binary Image. Bottom Right: Structuring Element in Comparison to Greyscale Image (Above) and Cross-Section (Below).}
\label{structuring element figure}
\end{figure}

@@

In binary erosion, erosion is accomplished by placing the origin of the structuring element over every pixel of the foreground regions in turn. If every point within the structuring element is in line with a foreground pixel, the foreground pixel lined up with the origin of the structuring element is left unchanged. If at least one point within the structuring element is in line with a background pixel, then the pixel lined up with the origin of the structuring element is converted to a background pixel~\cite{MorphologyWiki}. An example of binary erosion on a 30x20 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary erosion figure}. The erosion of foreground regions is equivalent to the dilation (discussed in Subsection~\ref{dilation}) of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 6.75in 0 0},clip]{erosion}
\caption{Binary Erosion: Left: Original Image. Center: Erosion Marked. Right: Results of Erosion.}
\label{binary erosion figure}
\end{figure}

Gray scale erosion follows the same basic pattern, but is somewhat more complex. Here, the origin of the structuring element is placed in line with a pixel on or below the surface. If every point within the structuring element is also either on or below the surface, the pixel lined up with the origin is left unchanged. If at least one point within the structuring element is above the surface, the pixel lined up with the origin of the structuring element is essentially removed (set to be above the surface). This process is repeated for every pixel on or below the surface~\cite{MorphologyPaper:1987, MorphologyWiki}. An example of greyscale erosion performed on a cross-section of an 11x32 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{greyscale erosion figure}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4in 0 0},clip]{greyscale_erosion}
\caption{Greyscale Erosion: Top: Original Image. Center Left: Cross-Section of Image Surface. Center Center: Erosion Marked. Center Right: Erosion of Surface. Bottom: Results of Erosion.}
\label{greyscale erosion figure}
\end{figure}

@@

In binary dilation, this is accomplished by placing the origin of the structuring element over every pixel of the background regions in turn. If every point within the structuring element is in line with a background pixel, the background pixel lined up with the origin of the structuring element is left unchanged. If at least one point within the structuring element is in line with a foreground pixel, then the pixel lined up with the origin of the structuring element is converted to a foreground pixel~\cite{MorphologyWiki}. An example of binary dilation on a 30x20 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary dilation figure}. The dilation of foreground regions is equivalent to the erosion (discussed in Subsection~\ref{erosion}) of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 6.75in 0 0},clip]{dilation}
\caption{Binary Dilation: Left: Original Image. Center: Dilation Marked. Right: Results of Dilation.}
\label{binary dilation figure}
\end{figure}

Like greyscale erosion, greyscale dilation is a more complex variation its binary counterpart. Here, the origin of the structuring element is placed in line with a pixel above the surface. If every point within the structuring element is also above the surface, the pixel lined up with the origin is left unchanged. If at least one point within the structuring element is on or below the surface, the pixel lined up with the origin of the structuring element is set to be on or below the surface. This process is repeated for every pixel above the surface~\cite{MorphologyPaper:1987, MorphologyWiki}. An example of greyscale dilation performed on a cross-section of an 11x32 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{greyscale dilation figure}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4in 0 0},clip]{greyscale_dilation}
\caption{Greyscale Dilation: Top: Original Image. Center Left: Cross-Section of Image Surface. Center Center: Dilation Marked. Center Right: Dilation of Surface. Bottom: Results of Dilation.}
\label{greyscale dilation figure}
\end{figure}

\subsection{Opening}\label{opening}
The opening of an image is an erosion followed by a dilation, and is denoted by the equation
\begin{equation*}
g = f \circ s = (f \ominus s) \oplus s
\end{equation*}
where the symbol $\circ$ indicates opening~\cite{MorphologyWikiAnonymous, MorphologyBook:2000}. Similar to erosion, opening strips away foreground pixels at the boundaries of foreground regions, but is less destructive of the initial foreground regions than erosion. Opening is therefore typically used to preserve foreground regions with a similar size and shape to the structuring element, while removing or reducing other foreground regions~\cite{MorphologyWiki}. An example of binary opening on a 30x20 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary opening figure}. The opening of foreground regions is equivalent to the closing of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4.75in 0 0},clip]{opening}
\caption{Opening: Left: Original Image. Second from Left: Erosion Marked. Center: Results of Erosion. Second from Right: Dilation Marked. Right: Results of Dilation (Opening Complete).}
\label{binary opening figure}
\end{figure}

@@

\subsection{Closing}\label{closing}
Closing of an image is a dilation followed by an erosion, and is denoted by the equation
\begin{equation*}
g = f \bullet s = (f \oplus s) \ominus s
\end{equation*}
where the symbol $\bullet$ indicates closing~\cite{MorphologyWikiAnonymous, MorphologyBook:2000}. Similar to dilation, closing adds foreground pixels at the boundaries of foreground regions, but is less destructive of the initial background regions than dilation. Closing is therefore typically used to preserve background regions with a similar size and shape to the structuring element, while removing or reducing other background regions~\cite{MorphologyWiki}. An example of binary closing on a 30x20 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary closing figure}. The closing of foreground regions is equivalent to the opening of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4.75in 0 0},clip]{closing}
\caption{Closing: Left: Original Image. Second from Left: Dilation Marked. Center: Results of Dilation. Second from Right: Erosion Marked. Right: Results of Erosion (Closing Complete).}
\label{binary closing figure}
\end{figure}

The greyscale closing of an image also consists of a dilation followed by an erosion. In this situation, however, both the dilation and erosion are greyscale rather than binary~\cite{MorphologyPaper:1987}.

@@

\subsubsection{Multiscale Top-Hat}\label{multiscale top-hat}
Subsubsections~\ref{black top-hat} and \ref{white top-hat} explain classical top-hat transforms. While these are popular and frequently used, they are not perfect. Paintings often contain details (such as fine brush strokes) which are misinterpreted as cracks by these filters. The multiscale morphological top-hat transform may be used to counteract this, as well as to detect cracks of varying sizes~\cite{Altarpiece:2013}. This transformation is executed by performing a series of classical top-hat transforms with structuring elements of various shapes and sizes (Cornelis et al use square structuring elements "ranging from 3x3 to \textit{n}x\textit{n} pixels, where \textit{n} depends on the width of the crack to be detected"~\cite{Altarpiece:2013}). The resulting images, or crack maps, are then further processed to remove isolated groups of pixels and bridge pixel gaps.

@@

The statistics reported are summarized in Table~\ref{results table}. While the true positive rate, or recall, recorded by Karianakis and Maragos is proportional to that of the top-hat transform when the percentage of edge information lost is low, the alternative very quickly losses any comparability as the percentage of edge information lost increases. And while the precision does increase as edge information is lost, even the highest precision demonstrated by the alternative does not compare with the precision of the top-hat transform. It is therefore reasonable to conclude that the top-hat transform, in both its classical and multiscale forms, significantly outperforms the alternative implemented by Karianakis and Maragos.
\begin{table}
\centering

\resizebox{8.5cm}{!}{
\begin{tabular}{|l|l|r|r|r|r|r|r|r|}
\hline
\textbf{Method} & \textbf{Classification} & \textbf{\textit{tp}} & \textbf{\textit{fn}} & \textbf{\textit{tn}} & \textbf{\textit{fp}} & \textbf{\textit{TP} (or \textit{R})} & \textbf{\textit{FP}} & \textbf{\textit{P}}\\ \hline
\multirow{8}{*}{Top-Hat Transform}
& Crack Thickness - Thin & 220 & 30 & 230 & 20 & 0.880 & 0.080 & 0.917\\ \cline{2-9}
& Crack Thickness - Medium & 232 & 18 & 231 & 19 & 0.928 & 0.076 & 0.924\\ \cline{2-9}
& Crack Thickness - Thick & 235 & 15 & 238 & 12 & 0.940 & 0.048 & 0.951\\ \cline{2-9}
& Number of Cracks - Few & 242 & 8 & 245 & 5 & 0.968 & \textbf{0.020} & 0.980\\ \cline{2-9}
& Number of Cracks - Medium & 245 & 5 & 241 & 9 & \textbf{0.980} & 0.036 & 0.965\\ \cline{2-9}
& Number of Cracks - Many & 243 & 7 & 243 & 7 & 0.972 & 0.028 & 0.972\\ \cline{2-9}
& Crack Connectivity - Low & 215 & 35 & 219 & 31 & \textbf{0.860} & \textbf{0.124} & 0.874\\ \cline{2-9}
& Crack Connectivity - High & 218 & 32 & 221 & 29 & 0.872 & 0.116 & 0.883\\ \hline
\multirow{3}{*}{Alternative Method}
& Edge Information Lost - 1\% & - & - & - & - & \textbf{0.932} & - & \textbf{0.497}\\ \cline{2-9}
& Edge Information Lost - 30\% & - & - & - & - & 0.857 & - & 0.594\\ \cline{2-9}
& Edge Information Lost - 70\% & - & - & - & - & \textbf{0.530} & - & \textbf{0.704}\\ \hline
\end{tabular}
}
\caption{Crack Detection Results by Methodology: Results Specified in Text Emphasized, Modified from~\cite{Statistics:2013, Theran:2013}.}
\label{results table}
\end{table}

>>>>

\section{Morphological Operations}\label{morphological operations}
Following optional edge detection is crack detection, the focus of this paper. However, in order to understand this stage, it is first necessary to describe the basic principles of mathematical morphology. Typically, morphology is used in processing binary (black and white) images, although there are also variations used for greyscale images. This paper will examine both variations. Morphological functions take two inputs. The first input is the image to be processed. In binary morphology, the input image is divided into foreground (typically white) and background (typically black) regions. In greyscale morphology, the image is treated as a three-dimensional object, where higher areas are brighter (white) and lower areas are darker (black). The second input is a structuring element, a (typically small, in comparison to the image) set of coordinate points. An example of a 3x3 square structuring element with the origin located at the center in comparison to both a 20x30 binary image and a 32x11 greyscale image is presented in Figure~\ref{structuring element figure}. The structuring element is then used to modify the input image. The image that results from the morphological operation is determined by the shape, size, and point of origin of the structuring element~\cite{MorphologyWikiAnonymous, MorphologyBook:2000, MorphologyPaper:1987, MorphologyWiki}. Subsections~\ref{erosion}, \ref{dilation}, \ref{opening}, and \ref{closing} explain the fundamental operations of mathematical morphology.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 6.5in 0 0},clip]{structuring_element}
\caption{Structuring Elements: Top: Structuring Element. Bottom Left: Structuring Element in Comparison to Binary Image. Bottom Right: Structuring Element in Comparison to Greyscale Image (Above) and Cross-Section (Below).}
\label{structuring element figure}
\end{figure}

@@

In binary erosion, erosion is accomplished by placing the origin of the structuring element over every pixel of the foreground regions in turn. If every point within the structuring element is in line with a foreground pixel, the foreground pixel lined up with the origin of the structuring element is left unchanged. If at least one point within the structuring element is in line with a background pixel, then the pixel lined up with the origin of the structuring element is converted to a background pixel~\cite{MorphologyWiki}. An example of binary erosion on a 20x30 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary erosion figure}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 6.75in 0 0},clip]{erosion}
\caption{Binary Erosion: Left: Original Image. Center: Erosion Marked. Right: Results of Erosion.}
\label{binary erosion figure}
\end{figure}

Greyscale erosion follows the same basic pattern, but is somewhat more complex. Recall that in greyscale morphology, the image is viewed as a three-dimensional object, with ``hills'' corresponding to higher intensities and ``valleys'' indicating lower intensities. Here, the origin of the structuring element is placed in line with a pixel within the object. If every point within the structuring element is contained within the object, the pixel lined up with the origin is left unchanged. If at least one point within the structuring element is outside the object, the pixel lined up with the origin of the structuring element is removed. This process is repeated for every pixel within the object~\cite{MorphologyPaper:1987, MorphologyWiki}. An example of greyscale erosion performed on a cross-section of a 32x11 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{greyscale erosion figure}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4in 0 0},clip]{greyscale_erosion}
\caption{Greyscale Erosion: Top: Original Image. Center Left: Cross-Section of Image Surface. Center Center: Erosion Marked. Center Right: Erosion of Surface. Bottom: Results of Erosion.}
\label{greyscale erosion figure}
\end{figure}

@@

In binary dilation, this is accomplished by placing the origin of the structuring element over every pixel of the background regions in turn. If every point within the structuring element is in line with a background pixel, the background pixel lined up with the origin of the structuring element is left unchanged. If at least one point within the structuring element is in line with a foreground pixel, then the pixel lined up with the origin of the structuring element is converted to a foreground pixel~\cite{MorphologyWiki}. An example of binary dilation on a 20x30 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary dilation figure}. The dilation of foreground regions is equivalent to the erosion (discussed in Subsection~\ref{erosion}) of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 6.75in 0 0},clip]{dilation}
\caption{Binary Dilation: Left: Original Image. Center: Dilation Marked. Right: Results of Dilation.}
\label{binary dilation figure}
\end{figure}

Like greyscale erosion, greyscale dilation is a more complex variation on its binary counterpart. Once again, the origin of the structuring element is placed in line with a pixel within the three-dimensional object that represents the original image. If every point within the structuring element is contained within the object, the object is left unchanged. If at least one point within the structuring element is outside the object, the regions outside of the object lined up with points within the structuring element are set to be a part of the object. This process is repeated for every pixel within the object~\cite{MorphologyPaper:1987, MorphologyWiki}. An example of greyscale dilation performed on a cross-section of a 32x11 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{greyscale dilation figure}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4in 0 0},clip]{greyscale_dilation}
\caption{Greyscale Dilation: Top: Original Image. Center Left: Cross-Section of Image Surface. Center Center: Dilation Marked. Center Right: Dilation of Surface. Bottom: Results of Dilation.}
\label{greyscale dilation figure}
\end{figure}

\subsection{Opening}\label{opening}
The opening of an image is an erosion followed by a dilation, and is denoted by the equation
\begin{equation*}
g = f \circ s = (f \ominus s) \oplus s
\end{equation*}
where the symbol $\circ$ indicates opening~\cite{MorphologyWikiAnonymous, MorphologyBook:2000}. Similar to erosion, opening strips away foreground pixels at the boundaries of foreground regions, but is less destructive of the initial foreground regions than erosion. Opening is therefore typically used to preserve foreground regions with a similar size and shape to the structuring element, while removing or reducing other foreground regions~\cite{MorphologyWiki}. An example of binary opening on a 20x30 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary opening figure}. The opening of foreground regions is equivalent to the closing of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4.75in 0 0},clip]{opening}
\caption{Opening: Left: Original Image. Second from Left: Erosion Marked. Center: Results of Erosion. Second from Right: Dilation Marked. Right: Results of Dilation (Opening Complete).}
\label{binary opening figure}
\end{figure}

@@

\subsection{Closing}\label{closing}
Closing of an image is a dilation followed by an erosion, and is denoted by the equation
\begin{equation*}
g = f \bullet s = (f \oplus s) \ominus s
\end{equation*}
where the symbol $\bullet$ indicates closing~\cite{MorphologyWikiAnonymous, MorphologyBook:2000}. Similar to dilation, closing adds foreground pixels at the boundaries of foreground regions, but is less destructive of the initial background regions than dilation. Closing is therefore typically used to preserve background regions with a similar size and shape to the structuring element, while removing or reducing other background regions~\cite{MorphologyWiki}. An example of binary closing on a 20x30 image using a 3x3 square structuring element with the origin located at the center is presented in Figure~\ref{binary closing figure}. The closing of foreground regions is equivalent to the opening of background regions~\cite{MorphologyWiki}.
\begin{figure}
\centering
\includegraphics[width=3in,trim={0 4.75in 0 0},clip]{closing}
\caption{Closing: Left: Original Image. Second from Left: Dilation Marked. Center: Results of Dilation. Second from Right: Erosion Marked. Right: Results of Erosion (Closing Complete).}
\label{binary closing figure}
\end{figure}

The greyscale closing of an image also consists of a dilation followed by an erosion. Here, however, both the dilation and erosion are greyscale rather than binary~\cite{MorphologyPaper:1987}.
\pagebreak

@@

\subsubsection{Multiscale Top-Hat}\label{multiscale top-hat}
Subsubsections~\ref{black top-hat} and \ref{white top-hat} explain classical top-hat transforms. While these are popular and frequently used, they are not perfect. Paintings often contain details (such as fine brush strokes) which are misinterpreted as cracks by these filters. The multiscale morphological top-hat transform may be used to counteract this, as well as to detect cracks of varying sizes~\cite{Altarpiece:2013}. This transformation is executed by performing a series of classical top-hat transforms with structuring elements of various shapes and sizes (Cornelis et al use square structuring elements ``ranging from 3x3 to \textit{n}x\textit{n} pixels, where \textit{n} depends on the width of the crack to be detected''~\cite{Altarpiece:2013}). The resulting images, or crack maps, are then further processed to remove isolated groups of pixels and bridge pixel gaps.

@@

The statistics reported are summarized in Table~\ref{results table}. While the true positive rate, or recall, recorded by Karianakis and Maragos is proportional to that of the top-hat transform when the percentage of edge information lost is low, the alternative very quickly losses any comparability as the percentage of edge information lost increases. And while the precision does increase as edge information is lost, even the highest precision demonstrated by the alternative does not compare with the precision of the top-hat transform. It is therefore reasonable to conclude that the top-hat transform, in both its classical and multiscale forms, significantly outperforms the alternative implemented by Karianakis and Maragos.
\begin{table*}
\centering
%\resizebox{8.5cm}{!}{
\begin{tabular}{|l|l|r|r|r|r|r|r|r|}
\hline
\textbf{Method} & \textbf{Classification} & \textbf{\textit{tp}} & \textbf{\textit{fn}} & \textbf{\textit{tn}} & \textbf{\textit{fp}} & \textbf{\textit{TP} (or \textit{R})} & \textbf{\textit{FP}} & \textbf{\textit{P}}\\ \hline
\multirow{8}{*}{Top-Hat Transform}
& Crack Thickness - Thin & 220 & 30 & 230 & 20 & 0.880 & 0.080 & 0.917\\ \cline{2-9}
& Crack Thickness - Medium & 232 & 18 & 231 & 19 & 0.928 & 0.076 & 0.924\\ \cline{2-9}
& Crack Thickness - Thick & 235 & 15 & 238 & 12 & 0.940 & 0.048 & 0.951\\ \cline{2-9}
& Number of Cracks - Few & 242 & 8 & 245 & 5 & 0.968 & \textbf{0.020} & 0.980\\ \cline{2-9}
& Number of Cracks - Medium & 245 & 5 & 241 & 9 & \textbf{0.980} & 0.036 & 0.965\\ \cline{2-9}
& Number of Cracks - Many & 243 & 7 & 243 & 7 & 0.972 & 0.028 & 0.972\\ \cline{2-9}
& Crack Connectivity - Low & 215 & 35 & 219 & 31 & \textbf{0.860} & \textbf{0.124} & 0.874\\ \cline{2-9}
& Crack Connectivity - High & 218 & 32 & 221 & 29 & 0.872 & 0.116 & 0.883\\ \hline
\multirow{3}{*}{Alternative Method}
& Edge Information Lost - 1\% & - & - & - & - & \textbf{0.932} & - & \textbf{0.497}\\ \cline{2-9}
& Edge Information Lost - 30\% & - & - & - & - & 0.857 & - & 0.594\\ \cline{2-9}
& Edge Information Lost - 70\% & - & - & - & - & \textbf{0.530} & - & \textbf{0.704}\\ \hline
\end{tabular}
%}
\caption{Crack Detection Results by Methodology: Data Specified in Text Emphasized, Modified from~\cite{Statistics:2013, Theran:2013}.}
\label{results table}
\end{table*}
